Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-02 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
working on hypotheses/ predictions

**2. Which species functional traits predict drought response (and which are the best predictors)?**

@@

 2.2.

**3. How are functional traits distributed across size classes, and how does this affect size-resistance relationship?**  ([issue #43](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/43))

3.1. Larger/ more exposed trees have more drought resistant traits, meaning size effects are buffered by traits  
3.1_alt. Larger trees suffer more because they have more drought vulnerable traits.

     * P3.1a- TLP is lower (larger negative) in taller/canopy trees
     * P3.1b- diffuse porous species more common in understory

     * P3.2- Inclusion of TLP / rp in model does not eliminate or significantly reduce effect of tree size.

>>>>

**2. How do species' traits--alone and in interaction with tree size--influence drought response?**

@@

2.2. Traits vary with microenvironment, with more drought-resistant traits associated to taller trees (and drier topographic positions) ([issue #43](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/43))

     * P2.2a- traits (all 5 above) correlate with tree height 
     * (P2.2b- traits (all 5 above) correlate with TWI)

2.3. Size-dependent drought resistance is driven by--or alternatively, buffered by--functional traits (i.e., larger trees have more drought vulnerable traits).
    * P3.1 Inclusion of traits in the statistical model does not eliminate or significantly reduce effect of tree size (or TWI).
